Tidal streams in triaxial systems

### 2015-02-16 ms.tex
werqin

% Affiliations
\newcommand{\colum}{1}
\newcommand{\adrn}{2}
\newcommand{\mich}{3}
\altaffiltext{\colum}{Department of Astronomy, 
		              Columbia University, 
		              550 W 120th St., 
		              New York, NY 10027, USA}
\altaffiltext{\adrn}{To whom correspondence should be addressed: adrn@astro.columbia.edu}
\altaffiltext{\mich}{ }

@@

On the largest scales ($\gtrsim$30~kpc for a Milky-Way-like galaxy) in the halos of galaxies, gravitational potentials are thought to be triaxial. However, despite suggestive evidence, this fundamental prediction from $\Lambda$CDM cosmology has not been conclusively confirmed from observations. Around other galaxies, it is generally hard to measure the 3D mass profile because they are seen in projection. From our position within the Milky Way, our view of our own halo and proximity gives us a unique chance to directly measure the 6D positions of stars and model the shape of the mass distribution at large radii. Unfortunately, the Milky Way halo has a low density of visible tracers. Luckily, however, many of the halo stars are likely associated with debris stripped from in-falling satellite galaxies.

As a satellite galaxy or globular cluster orbits within some larger system, mass is eroded due to the tidal forces of the host galaxy potential. If the orbit of such an object is regular, only mildly eccentric, and stays far from sharp density features (e.g., the disk), the disruption is a steady process and the mass is slowly stretched into long streams of matter. The phase-space density and therefore the observable properties of these tidal streams are sensitive to the internal progenitor properties, orbit of the progenitor, and underlying mass distribution of the host galaxy. The morphological evolution of the debris depends on the spread of orbital properties (e.g., actions) of the debris and the orbit of the progenitor system, both of which are determined by the shape and radial profile of the gravitational potential of the host galaxy. In the halo of the Milky Way, tidal streams of stars are found over a large range of distances ($\sim$10-100~kpc). By simultaneously modeling the observed phase-space density of stream stars along with the potential, it is hoped that we may infer the dark matter distribution of the Milky Way on these large scales.

Tidal streams are generally modeled as inherently 1D structures formed on regular orbits with simple internal progenitor dynamics and density evolution. Methods span a range of complexity from orbit-fitting, to \emph{Streakline} or particle-spray models, to action-space density modeling, to direct $N$-body simulations. All methods have been tested in some way on simulated observations of data and authors have mainly demonstrated their ability to recover parameters of analytic, static potential forms. Many of the methods have been [...] in axisymmetric or otherwise simple potentials but claim to extend to more complex, generalized potentials (e.g., triaxial of multi-component potentials).

\citet{pearson15} tried to reproduce observations of the stellar stream density from the globular cluster Palomar 5 in a single oblate and single triaxial potential using \emph{Streakline} models \citep{kupper12}. They use the observed SDSS number density of stars and a limited number of radial velocities measured for stream members to fit their models to the data. In the oblate potential (a three-component, bulge, disk, and spherical halo potential), a thin model stream is easily found that reproduces the observed stellar density morphology of the stream. In the triaxial potential (the potential fit to the Sagitarrius stream by \cite{law10}), the model streams generically form large, two-dimensional ``fans'' of debris near the ends, and there are no physically reasonable progenitor orbits that reproduce the observed thinness of the stream, given the observational constraints of the present-day position and velocity of the cluster. This result suggests that the shape of the host galaxy potential directly influences the morphology of the resulting debris. In order to extending tidal stream models to more generic potentials, it is important to understand why this stream-fanning occurs and whether this and other strange debris morphologies are generic to more complex potentials.

One obvious difference between the two potentials considered in \citet{pearson15} is the extra symmetry of the oblate potential. For an integrable Hamiltonian, $H$, with $N$ degrees of freedom (dof), the equations of motion are most simply expressed in angle-action coordinates. In these coordinates, the actions, $J_n$, are integrals of the motion, and the conjugate angle variables, $\theta_n$, increase linearly with time
\begin{align}
	\act_n &= {\rm const.}\\
	\dot{\act}_n &= -\frac{\partial H}{\partial \theta_n} = 0\\
	\theta_n(t) &= \Omega_n t + \theta_n(0)\\
	\dot{\theta}_n &= \frac{\partial H}{\partial \act_n} = \Omega_n(\act_1,\act_2,...,\act_n)\label{eq:aafreq}
\end{align}
where $i=1,2,...N$, and $\Omega_n$ are the fundamental frequencies of the orbit. Owing to the involutive property of the actions and the periodic nature of the angle variables, the topology of angle-action space is equivalent to that of the surface of an $N$-dimensional torus, and thus orbits are often referred to in terms of \emph{orbital tori}: each set of actions, $(\act_1,\act_2,...\act_N)$, uniquely determine the torus associated with a given orbit and the angles specify the location on the surface of the $N$-torus.

If, to first order, galactic halos are triaxial, galactic gravitational potentials will almost certainly not be globally integrable. If a triaxial potential is close to integrable such that the Hamiltonian can be written in terms of a small perturbation, $\epsilon$, away from some integrable Hamiltonian, $H_0$,
\begin{equation}
	H(\bs{\theta}, \bs{\act}) = H_0(\bs{\act}) + \epsilon H_1(\bs{\theta}, \bs{\act})
\end{equation}
then a large number of regular orbits will survive the perturbation (by way of the KAM theorem)\footnote{3-vectors are represented with bold symbols, e.g., $\bs{J}=(J_1,J_2,J_3)$.}. The tori that survive will in general be separated by regions of irregular or chaotic motion, and thus any transformations to angle-action coordinates can only be defined locally.

@@

For small potential perturbations, many regular orbits survive and only small chaotic islands are introduced. As the strength of the perturbation increases, eventually all tori associated with conditionally-periodic motion will be destroyed. Next, the uni-resonant tori are destroyed, and finally the bi-resonant tori -- these are least susceptible to destruction from perturbations \citep[e.g., see][]{valluri98}. However, even orbits that are strictly chaotic may behave regularly over timescales much longer than, e.g., the dynamical time of the system. Chaotic can therefore be loosely classified by being either \emph{strongly} or \emph{weakly} chaotic: strongly chaotic orbits behave irregularly over a few ($\sim$10) dynamical times, whereas weakly chaotic orbits behave regularly over this timescale (we quantify this distinction in Section~\ref{sec:}). This rough classification is tied to local measures, such as the Lyapunov time (Section~\ref{}) or frequency diffusion time (Section~\ref{}), and to the mixing rate of small ensembles of orbits (Section~\ref{}).

@@

All of these parameters are specified in terms of the \emph{density}; for orbit analysis, we need to determine the form of the potential in terms of these parameters, which, in general, requires numerical integration of the density at each position of interest. For computational efficiency, many authors instead express the triaxiality in the form of the potential, however this can lead to unphysical situations where the density becomes negative. \citet{leesuto03} derive a perturbative expansion of the potential integral for a triaxial NFW density and show that the expansion is accurate even for modest axis ratios (e.g., the median values shown above).

@@

This potential is a simple and unrealistic model for the total potential of a Milky-Way-like galaxy, however it represents a conservative choice for exploring the effect of chaos in the halos of such galaxies. Real galactic potentials will have a significant component due to the disk and bulge and may have twisting inertia tensors (cite), radially changing axis ratios \citep[e.g.,][]{veraciro11}, significant substructure \citep{zemp09}, or time dependence (either from bulk rotation, mass growth, mergers, etc.; cite). We expect all of these effects to increase the amount and influence of chaos; see the Discussion (Section~\ref{sec:discussion}) for a few simple examples that demonstrate this expectation.

@@

We use the Dormand-Prince 8th-order Runge-Kutta scheme (cite Dormand 1981) to integrate orbits in the above potential. In particular, we use the Python wrapper to the FORTRAN routines provided in the Scipy package \citep{scipy}. For all orbits, we ensure that energy is conserved to $\Delta E/E_0 \leq 10^{-9}$ by the end of integration. Unless otherwise specified, orbits are integrated for $\sim$200 orbital periods with 500 steps per orbital period. Some box orbits require more internal integration steps in order to conserve energy to the required level.

@@

Computing the Lyapunov spectrum for a given orbit is often not necessary if one is only interested in characterizing the degree of chaos. Instead, it is often more efficient to compute the maximum Lyapunov exponent by estimating the finite-time maximum Lyapunov exponent (FTMLE), defined as 
\begin{equation}
	l_{\rm max}(t) = \frac{1}{t}\ln \frac{\|\delta \bs{w}(t)\|}{\|\delta \bs{w}_0\|}.\label{eq:lmax}
\end{equation}
The maximum Lyapunov exponent is the limit as $t\rightarrow \infty$ of the FTMLE
\begin{equation}
	\lambda_{\rm max} = \lim_{t\rightarrow\infty}l_{\rm max}(t). \label{eq:lyapmax}
\end{equation}
Numerically computing this quantity is not trivial because (1) obviously the limit to infinity is not possible and (2) the norm of the deviation vector $\|\delta \bs{w}(t)\|$ is expected to increase exponentially for chaotic orbits, leading to numerical problems. To circumvent these issues, it is sufficient to instead start a nearby orbit with some small initial deviation with norm $\delta_0$, integrate for a sufficiently small amount of time, $\tau$, then renormalize the deviation back to the initial norm (e.g., cite Bennetin et al. 1976, Tabor 1989). The following pseudocode outlines this procedure:\footnote{see Gary for Python implementation?}\\
\begin{algorithmic}[1]
\State {\bf define} orbital integration timestep, $h$, and number of steps, $K$
\State {\bf define} initial norm of deviation vector, $\delta_0$, to be sufficiently small
\State {\bf define} renormalization integration period, $\tau \ll hK$ 
\For{each timestep when integrating the main orbit, $\bs{w}(t)$}
\State step forward the orbit and deviation vector orbit by one timestep, $t_{i-1} \rightarrow t_i$
\If {a normalization timestep}
\State measure and store the length of the deviation vector, $\delta_i = \|\delta \bs{w}_i\|$
\State renormalize the length of the deviation vector, $\delta \bs{w}_i = \delta \bs{w}_i (\delta_0/\delta_i)$
\EndIf
\EndFor 
\end{algorithmic}
The FTMLE after a given number of timesteps, $N$, is then estimated as
\begin{equation}
	l_N = \frac{1}{N\tau}\sum_i^N \ln \, \delta_i
\end{equation}
and the MLE is
\begin{equation}
	\lambda_{\rm max} = \lim_{N\rightarrow \infty} l_N.
\end{equation}
[Some more practical issues with implementation] [Figure showing $l_N$ for regular, chaotic orbit?]

@@

NAFF has been applied to many problems in Solar System and Galactic dynamics, especially in the study of of orbits in triaxial systems. For more details about the method, see \cite{papaphillipou, laskar, etc.}. We have implemented and tested our own implementation of NAFF in Python. This code is publicly available through the Gary package.\footnote{link to repo} Figure~\ref{fig:logfreqs} shows a test of the implementation in which we reproduce the frequency map at a fixed energy of an axisymmetric, logarithmic potential \cite[][pg. 260, Figure~3.45]{binneytremaine}. Plotted are the (Cartesian) frequency ratios recovered for a grid of iso-energy, box orbits integrated in the potential $\Phi(x,y,z) = \frac{1}{2}\ln\left(x^2 + (y/0.9)^2 + (z/0.7)^2 + 0.1\right)$. In such a map, stable resonances appear as linear over-densities and unstable resonances appear as linear under-densities.

@@

Our goal is to characterize the morphology of tidal debris along orbits generic to triaxial potentials. For example, it has been shown that along some chaotic orbits, tidal streams form large, diffuse ``fans'' of debris \citep[e.g.][]{pearson15, fardal??} [TODO: should I put sarahs paper here even though we didn't say this explicitly?], however, it is unknown how the resultant properties of the debris (e.g., density or length of the stream) depend on the degree of stochasticity. Further, quantifying the degree of stochasticity with, for example, the frequency diffusion rate represents a \emph{local} measure of chaos and it is unclear how this generalizes to the small but finite spreads in orbital characteristics common to debris that is tidally disrupted from globular clusters or dwarf satellite galaxies. To answer this question would require a massive exploration of parameter space -- both in potential and in orbits -- and thus would require a prohibitive number of N-body simulations to truly analyze the disruption process in all situations.

@@

The majority of the orbits generated on these grids are tube orbits, which preserve a sense of rotation about one of the principal axes of the potential and are generally centrophobic. Tube orbits are generally less stochastic than box orbits -- the other major class of orbits in triaxial potentials -- which tend to plunge deep into the inner regions of the potential. Thin tidal streams are thought to form along tube orbits rather than box orbits because of the fast disruption expected for stellar systems on radially plunging orbits. The major classes of stable tube orbits circulate about either the major or minor axis; the most prominent orbits are the short-axis and outer long-axis tubes, but these grids do generate some inner long-axis tubes and box orbits. Orbits that try to circulate about the intermediate axis tend to be highly irregular and do not preserve their sense of circulation for long periods of time. NAFF recovers fundamental frequencies for an orbit faster (with a fewer number of terms) when the coordinates used are ``close'' to the angle variables \cite[PL95][]{papaphillippou96}. PL96 show that a good choice of coordinates for tube orbits are the Poincar\'e symplectic polar coordinates, a set of canonical coordinates similar to cylindrical coordinates. For approximately XX\% of the orbits, NAFF fails to recover the frequencies (similar difficulties were reported in \cite{valluri98} and \cite{papaphillippou96} for recovering certain tube orbit frequencies).

>>>>

% Affiliations
\newcommand{\colum}{1}
\newcommand{\adrn}{2}
\newcommand{\mich}{3}
\altaffiltext{\colum}{Department of Astronomy, 
		              Columbia University, 
		              550 W 120th St., 
		              New York, NY 10027, USA}
\altaffiltext{\adrn}{To whom correspondence should be addressed: adrn@astro.columbia.edu}
\altaffiltext{\mich}{Department of Astronomy, 
			   University of Michigan,
			   Ann Arbor, MI 48109, USA}

@@

On the largest scales ($\gtrsim$30~kpc for a Milky-Way-like galaxy) in the halos of galaxies, gravitational potentials are thought to be triaxial. Despite suggestive evidence, this fundamental prediction from $\Lambda$CDM cosmology has not been conclusively confirmed from observations. Around other galaxies, it is generally hard to measure the 3D mass profile because they are seen in projection. From the Earth's position within the Milky Way, our view of our own halo and proximity gives us a unique chance to directly measure the 6D positions of stars and model the shape of the mass distribution at large radii. Unfortunately, the Milky Way halo has a low density of visible tracers, but luckily many of the halo stars are likely associated with debris stripped from in-falling satellite galaxies.

As a satellite galaxy or globular cluster orbits within some larger system, mass is eroded due to the tidal forces of the host galaxy potential. If the orbit of such an object is regular, only mildly eccentric, and stays far from sharp density features (e.g., the disk), the disruption is a steady process and the mass is slowly stretched into long streams of matter. The phase-space density and therefore the observable properties of these tidal streams are sensitive to the internal progenitor properties, orbit of the progenitor, and underlying mass distribution of the host galaxy. The morphological evolution of the debris depends on the spread of orbital properties (e.g., actions or frequencies) of the debris and the orbit of the progenitor system, both of which are set by the shape and radial profile of the gravitational potential of the host galaxy. In the halo of the Milky Way, tidal streams of stars are found over a large range of distances ($\sim$10-100~kpc). By simultaneously modeling the observed phase-space density of stream stars along with the potential, it is hoped that we may infer the dark matter distribution of the Milky Way on these scales.

Tidal streams are generally modeled as 1D structures formed on regular orbits with simple internal progenitor dynamics and density evolution. Methods span a range of complexity from orbit-fitting, to \emph{Streakline} or particle-spray models, to action-space density modeling, to direct $N$-body simulations. All methods have been tested in some way on simulated observations of data and authors have mainly demonstrated their ability to recover parameters of analytic, static potential forms. Many of the methods have been [...] in axisymmetric or otherwise simple potentials but claim to extend to more complex, generalized potentials (e.g., triaxial or multi-component potentials).

\citet{pearson15} tried to reproduce observations of the stellar stream density from the globular cluster Palomar 5 in a single oblate and single triaxial potential using \emph{Streakline} models \citep{kuepper12}. They use the observed SDSS number density of stars and a limited number of radial velocities measured for stream members to fit model streams to the data. In the oblate potential (a three-component, bulge, disk, and spherical halo potential), a thin model stream is easily found that reproduces the observed stellar density morphology of the stream. In the triaxial potential (the potential from \cite{law10}, a three component, bulge, disk, and triaxial halo fit to Sagitarrius stream data), the model streams generically form large, two-dimensional ``fans'' of debris near the ends, and there are no physically reasonable progenitor orbits that reproduce the observed thinness of the stream given the observational constraints of the present-day position and velocity of the cluster. This result suggests that the shape of the host galaxy potential directly influences the morphology of the resulting debris. In order to extend tidal stream models to more generic potentials, it is important to understand why this stream-fanning occurs and whether this and other strange debris morphologies are generic to more complex potentials.

One obvious difference between the two potentials considered in \citet{pearson15} is the extra symmetry of the oblate potential. For an integrable Hamiltonian, $H$, with $N$ degrees of freedom (dof), the equations of motion are most simply expressed in angle-action coordinates. In these coordinates, the actions, $J_n$, are integrals of the motion, and the conjugate angle variables, $\theta_n$, increase linearly with time
\begin{align}
	\act_n &= {\rm const.}\\
	\dot{\act}_n &= -\frac{\partial H}{\partial \theta_n} = 0\\
	\theta_n(t) &= \Omega_n t + \theta_n(0)\\
	\dot{\theta}_n &= \frac{\partial H}{\partial \act_n} = \Omega_n(\act_1,\act_2,...,\act_n)\label{eq:aafreq}
\end{align}
where $i=1,2,...N$, and $\Omega_n$ are the fundamental frequencies of the orbit. Owing to the involutive property of the actions and the periodic nature of the angle variables, the topology of angle-action space is equivalent to that of the surface of an $N$-dimensional torus, and thus orbits are often referred to in terms of \emph{orbital tori}: each set of actions, $(\act_1,\act_2,...\act_N)$, uniquely determine the torus associated with a given orbit and the angles specify the location on the surface of the $N$-torus. If a global transformation to angle-action coordinates exists, the potential is said to be ``integrable.''

If to first order galactic halos are triaxial, galactic gravitational potentials will almost certainly not be globally integrable. If a triaxial potential is close to integrable such that the Hamiltonian can be written in terms of a small perturbation, $\epsilon$, away from some integrable Hamiltonian, $H_0$,
\begin{equation}
	H(\bs{\theta}, \bs{\act}) = H_0(\bs{\act}) + \epsilon H_1(\bs{\theta}, \bs{\act})
\end{equation}
then a large number of regular orbits will survive the perturbation (by way of the KAM theorem)\footnote{3-vectors are represented with bold symbols, e.g., $\bs{J}=(J_1,J_2,J_3)$.}. The tori that survive will in general be separated by regions of irregular or chaotic motion, and thus any transformations to angle-action coordinates can only be defined locally. Analytic transformations to angle-action coordinates are only known for a handful of simple, integrable potentials. Much effort has gone in to developing general methods for transforming either from position-velocity to angle-action coordinates, $(\bs{x},\bs{v})\rightarrow(\bs{\theta},\bs{J})$ \citep{many}, or vice-versa, $(\bs{\theta},\bs{J})\rightarrow(\bs{x},\bs{v})$ \citep{many}.

@@

For small potential perturbations, many regular orbits survive and only small chaotic islands are introduced. As the strength of the perturbation increases, eventually all tori associated with conditionally-periodic motion will be destroyed. Next, the uni-resonant tori are destroyed, and finally the bi-resonant tori -- these are least susceptible to destruction from perturbations \citep[e.g., see][]{valluri98}. However, even orbits that are strictly chaotic may behave regularly over timescales much longer than, for example, the dynamical time of the system. Chaotic can therefore be loosely classified by being either \emph{strongly} or \emph{weakly} chaotic: strongly chaotic orbits behave irregularly over a few ($\sim$10) dynamical times, whereas weakly chaotic orbits behave regularly over this timescale (we quantify this distinction in Section~\ref{sec:}). This rough classification is tied to local measures, such as the Lyapunov time (Section~\ref{}) or frequency diffusion time (Section~\ref{}). In Section~\ref{} we look at how these relate to the the mixing rate of small ensembles of orbits.

@@

All of these parameters are specified in terms of the \emph{density}; for orbit analysis, we need to determine the form of the potential in terms of these parameters, which, in general, requires numerical integration of the density at each position of interest. For computational efficiency, many authors instead express the triaxiality in the form of the potential, but this can lead to unphysical situations where the density becomes negative. \citet{leesuto03} derive a perturbative expansion of the potential integral for a triaxial NFW density and show that the expansion is accurate even for modest axis ratios (e.g., the median values shown above).

@@

This potential is a simple and unrealistic model for the total potential of a Milky-Way-like galaxy, however it represents a conservative choice for exploring the effect of chaos in the halos of such galaxies. Real galactic potentials will have a significant component due to the disk and bulge and may have twisting inertia tensors (cite), radially changing axis ratios \citep[e.g.,][]{veraciro11}, significant substructure \citep{zemp09}, or time dependence (either from bulk rotation, mass growth, mergers, etc.; cite). We expect all of these effects to increase the amount and influence of chaos; see the Discussion (Section~\ref{sec:discussion}) for a few simple demonstrations.

@@

We use the Dormand-Prince 8th-order Runge-Kutta scheme (TODO: cite Dormand 1981) to integrate orbits in the above potential. In particular, we use the Python wrapper to the FORTRAN routines provided in the Scipy package \citep{scipy}. For all orbits, we ensure that energy is conserved to $\Delta E/E_0 \leq 10^{-9}$ by the end of integration. Unless otherwise specified, orbits are integrated for $\sim$200 orbital periods with 500 steps per orbital period. Some box orbits require more internal integration steps in order to conserve energy to the required level.

@@

Computing the Lyapunov spectrum for a given orbit is often not necessary if one is only interested in characterizing the degree of chaos. Instead, it is often more efficient to compute the maximum Lyapunov exponent by estimating the finite-time maximum Lyapunov exponent (FTMLE), defined as 
\begin{equation}
	l_{\rm max}(t) = \frac{1}{t}\ln \frac{\|\delta \bs{w}(t)\|}{\|\delta \bs{w}_0\|}.\label{eq:lmax}
\end{equation}
The maximum Lyapunov exponent is the limit as $t\rightarrow \infty$ of the FTMLE
\begin{equation}
	\lambda_{\rm max} = \lim_{t\rightarrow\infty}l_{\rm max}(t). \label{eq:lyapmax}
\end{equation}
Numerically computing this quantity is not trivial because (1) obviously the limit to infinity is not possible and (2) the norm of the deviation vector $\|\delta \bs{w}(t)\|$ is expected to increase exponentially for chaotic orbits, leading to numerical problems. To circumvent these issues, it is sufficient to instead start a nearby orbit with some small initial deviation with norm $\delta_0$, integrate for a sufficiently small amount of time, $\tau$, then renormalize the deviation back to the initial norm (e.g., cite Bennetin et al. 1976, Tabor 1989). 
%The following pseudocode outlines this procedure:\footnote{see Gary for Python implementation?}\\
%\begin{algorithmic}[1]
%\State {\bf define} orbital integration timestep, $h$, and number of steps, $K$
%\State {\bf define} initial norm of deviation vector, $\delta_0$, to be sufficiently small
%\State {\bf define} renormalization integration period, $\tau \ll hK$ 
%\For{each timestep when integrating the main orbit, $\bs{w}(t)$}
%\State step forward the orbit and deviation vector orbit by one timestep, $t_{i-1} \rightarrow t_i$
%\If {a normalization timestep}
%\State measure and store the length of the deviation vector, $\delta_i = \|\delta \bs{w}_i\|$
%\State renormalize the length of the deviation vector, $\delta \bs{w}_i = \delta \bs{w}_i (\delta_0/\delta_i)$
%\EndIf
%\EndFor 
%\end{algorithmic}
The FTMLE after a given number of timesteps, $N$, is then estimated as
\begin{equation}
	l_N = \frac{1}{N\tau}\sum_i^N \ln \, \delta_i
\end{equation}
and the MLE is
\begin{equation}
	\lambda_{\rm max} = \lim_{N\rightarrow \infty} l_N.
\end{equation}
[Some more practical issues with implementation] [Figure showing $l_N$ for regular, chaotic orbit?]

@@

NAFF has been applied to many problems in Solar System and Galactic dynamics, especially in the study of of orbits in triaxial systems. For more details about the method, see \cite{papaphilippou96, laskar, etc.}. We have implemented and tested our own implementation of NAFF in Python. This code is publicly available through the Gary package.\footnote{link to repo} Figure~\ref{fig:logfreqs} shows a test of the implementation in which we reproduce the frequency map at a fixed energy of an axisymmetric, logarithmic potential \cite[][pg. 260, Figure~3.45]{binneytremaine}. Plotted are the (Cartesian) frequency ratios recovered for a grid of iso-energy, box orbits integrated in the potential $\Phi(x,y,z) = \frac{1}{2}\ln\left(x^2 + (y/0.9)^2 + (z/0.7)^2 + 0.1\right)$. In such a map, stable resonances appear as linear over-densities and unstable resonances appear as linear under-densities.

@@

Our goal is to characterize the morphology of tidal debris along orbits generic to triaxial potentials. For example, it has been shown that along some chaotic orbits, tidal streams form large, diffuse ``fans'' of debris \citep[e.g.][]{pearson15, fardal14} [TODO: should I put sarahs paper here even though we didn't say this explicitly?], however, it is unknown how the resultant properties of the debris (e.g., density or length of the stream) depend on the degree of stochasticity. Further, quantifying the degree of stochasticity with, for example, the frequency diffusion rate represents a \emph{local} measure of chaos and it is unclear how this generalizes to the small but finite spreads in orbital characteristics common to debris that is tidally disrupted from globular clusters or dwarf satellite galaxies. To answer this question would require a massive exploration of parameter space -- both in potential and in orbits -- and thus would require a prohibitive number of N-body simulations to truly analyze the disruption process in all situations.

@@

The majority of the orbits generated on these grids are tube orbits, which preserve a sense of rotation about one of the principal axes of the potential and are generally centrophobic. Tube orbits are generally less stochastic than box orbits -- the other major class of orbits in triaxial potentials -- which tend to plunge deep into the inner regions of the potential. Thin tidal streams are thought to form along tube orbits rather than box orbits because of the fast disruption expected for stellar systems on radially plunging orbits. The major classes of stable tube orbits circulate about either the major or minor axis; the most prominent orbits are the short-axis and outer long-axis tubes, but these grids do generate some inner long-axis tubes and box orbits. Orbits that try to circulate about the intermediate axis tend to be highly irregular and do not preserve their sense of circulation for long periods of time. NAFF recovers fundamental frequencies for an orbit faster (with a fewer number of terms) when the coordinates used are ``close'' to the angle variables \cite[PL96][]{papaphilippou96}. PL96 show that a good choice of coordinates for tube orbits are the Poincar\'e symplectic polar coordinates, a set of canonical coordinates similar to cylindrical coordinates. For approximately XX\% of the orbits, NAFF fails to recover the frequencies (similar difficulties were reported in \cite{valluri98} and \cite{papaphilippou96} for recovering certain tube orbit frequencies).
